Regime transition identification for water utilization in river basin developments

### 2020-11-25 tex/sup/supplementary_information.tex
polished throughout along with the SI

\title{Regime transition identification for water utilization in river basin developments}
\author{Shuang Song, Shuai Wang, Bojie Fu, Xutong Wu (complete author list)}
\correspondingauthor{Shuai Wang.\\E-mail: shuaiwang@bnu.edu.cn}

@@

In general, there are inter-regional differences in the economic layout, distribution of water resources, distribution of water consumption, and population distribution of the Yellow River Basin (see Fig. S2). On the basis of these fundamental differences, social development and watershed management continue to influence and reshape their changes, making the Yellow River Basin the world's most intimately connected and dramatically changing large river basin. Thus, as a case study for analysing the evolution of the human-water relationship, it possesses typicality.

% \subsection*{Importance of water resource to society within the YRB}
Water resources make an irreplaceable contribution to the development of society in the YRB. Firstly, each aspect of economic development highly depended on water resources, since the most water use patterns are positively correlated with the region's key economic indicators (see Fig. S2-A, B and D). 
% Secondly, their relationships have noticeably changed over the study period. In particular, the major water-consuming sectors have undergone particularly dramatic changes (see Fig. S3-B).

@@

We list four main water-governance-related social transformations in table S3, here are explainations:

@@

% 补充图片3：天然水资源量
\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{../../figures/sup/sf_measured_runoff.pdf}
    \caption{Water resources in different regions. 
        \textbf{A,} changing trend of measured runoff, 
        \textbf{B, C and D} average measured runoff within different periods.
        \textbf{E, F and G} average total water consumptions within different periods. 
    }
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regimes and their main contributors.
		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		}
	\label{fig:dimensions}
\end{figure}

% 补充图片4：水资源灵活性
\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{../../figures/sup/inflexible_wu.pdf}
    \caption{
        Flexibility and its change contributions of water utilization.
        \textbf{A,} Proportion of inflexible water uses.
        \textbf{B,} Change contributions of inflexible water uses.
    }
\end{figure}

@@

% 补充图片6：用水比例
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../../figures/sup/sf_wu_sections_stackplot.jpg}
    \caption{Proportions of total water use between the different sectors}
\end{figure}

% 补充图片7：节水措施
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../../figures/sup/saving_water.jpg}
    \caption{
        Saving water irrigated area ratio in 2013.
    }
\end{figure}

@@

% 补充图片10：地下水
% \begin{figure}
%     \centering
%     \includegraphics[width=0.95\textwidth]{../../figures/sup/outages.jpg}
%     \caption{Severe runoff outages and groundwater depletion}
% \end{figure}

@@

>>>>

\title{Regime transition identification for water utilization in river basin developments}
\author{Shuang Song, Shuai Wang, Xutong Wu, Yongping Wei, Bojie Fu (complete author list)}
\correspondingauthor{Shuai Wang.\\E-mail: shuaiwang@bnu.edu.cn}

@@

In general, there are inter-regional differences in the economic layout, distribution of water resources, distribution of water consumption, and population distribution of the Yellow River Basin (see Fig. S2). On the basis of these fundamental differences, social development and watershed management continue to influence and reshape their changes, making the Yellow River Basin the world's most intimately connected and dramatically changing large river basin. Specially, Water resources make an irreplaceable contribution to the development of society in the YRB. Each sector of economic development highly depended on water resources, since the most water use patterns are positively correlated with the region's key economic indicators (see Fig. S3). Thus, as a case study for analysing the evolution of the human-water relationship, it possesses typicality.

% Secondly, their relationships have noticeably changed over the study period. In particular, the major water-consuming sectors have undergone particularly dramatic changes (see Fig. S3-B).

@@

We list four main water-governance-related social transformations in Fig 5D of the main text, here are explanations:

@@

% 补充图片3：用水比例
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../../figures/sup/sf_wu_sections_stackplot.jpg}
    \caption{Proportions of total water use between the different sectors}
\end{figure}

% 补充图片7：节水措施
\begin{figure}
    % TODO 这里还要增加一个过去的比例做对比
    \centering
    \includegraphics[width=0.6\textwidth]{../../figures/sup/saving_water.jpg}
    \caption{
        Saving water irrigated area ratio in 2013.
    }
\end{figure}

% 补充图片4：天然水资源量
\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{../../figures/sup/sf_measured_runoff.pdf}
    \caption{Water resources in different regions. 
        \textbf{A,} changing trend of measured runoff, 
        \textbf{B, C and D} average measured runoff within different periods.
        \textbf{E, F and G} average total water consumptions within different periods. 
    }
\end{figure}

@@

% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
% 	\caption{
% 		Changes in different dimensions of water resources utilization regimes and their main contributors.
% 		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
% 		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see \textit{SI Appendix} Methods S4).
% 		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
% 		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
% 		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
% 		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
% 		}
% 	\label{fig:dimensions}
% \end{figure}

@@

@@

% % 补充图片4：水资源灵活性
% \begin{figure}
%     \centering
%     \includegraphics[width=0.95\textwidth]{../../figures/sup/inflexible_wu.pdf}
%     \caption{
%         Flexibility and its change contributions of water utilization.
%         \textbf{A,} Proportion of inflexible water uses.
%         \textbf{B,} Change contributions of inflexible water uses.
%     }
% \end{figure}
